---
title: "Use buildReport() to Begin Writing Your Report"
date: "`r format(Sys.Date(), format='%B %d %Y') `"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{A_buildReport-elements}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  message = FALSE, echo = TRUE, warning = FALSE, 
  comment = FALSE, collapse = TRUE,
  comment = "#>"
)
options(rmarkdown.html_vignette.check_title = FALSE)

```

```{r setup}
library(NMFSReports)
library(here)
```


# Create initial structure of report

Do everyone here a favor and create a new r project or at least set up a working directory (`setwd()`). There will be a lot of file management here...

To build your intitial architecture for your new NOAA Tech Memo or Report, simply run the below script: 

## title

Default = "". Here, put the title of your report. You can change this later in the run file in needed.

```{r}
title = "My Awesome Report!"
```

## author

Here, add your First Lastname of everyone who is producing the report. You can change this later in the run file in needed.

```{r}
authors = "Me, Myself, and I"
```

## sections

Let's first think about what you want/need your Tech Memo to look like. For my purposes, I'll assume that you need the below sections:

```{r}
  # list the sections (that you will have different rmd scripts for) in order and with no spaces
sections <- c("frontmatter", # This is a specific template that matches the NOAA Template
               "abstract", # This, and all others unless otherwise mentioned, come from the same plain-slate document but are appropriately named and linked up in the 'run' file. 
               "introduction", 
               "methods", 
               "results", 
               "discussion", 
               "endmatter" # This is a specific template that will document all of your citations throughout the report, the R packages you used to create this report. I'm biased, but please give credit where credit is due! There are also spots here to list people's ORCID numbers and acknowlegements. 
              ) 
```

