---
title: "How to use the run.R file to be the skeleton of your report"
author: Emily Markowitz (Emily.Markowitz AT NOAA.gov / EmilyMarkowitz-NOAA)
date: "`r format(Sys.Date(), format='%B %d %Y') `"
output: 
  html_document:
    standalone: true
    smart: true
    normalize: true
    toc: true
    highlight: tango
    self-contained: true
    theme: cerulean
  pdf_document:
    toc: true
    highlight: tango
vignette: >
  %\VignetteIndexEntry{B_run-script-demo}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(message = FALSE, echo = TRUE, warning = FALSE, 
  collapse = TRUE,
  comment = "#>"
)

TF<-FALSE
```

```{r setup}
PKG <- c(# devtools::install_github("emilymarkowitz-NOAA/NMFSReports", force = TRUE)
         "NMFSReports",
         
         # Data Managment
         "tidyverse",
         "filesstrings", 
         "data.table", 
         "plyr",  
         "dplyr",
         
         # #RMarkdown
         "rmarkdown",
         "kableExtra"
)

for (p in PKG) {
  if(!require(p,character.only = TRUE)) {  
    install.packages(p, repos = "http://cran.us.r-project.org")
    require(p,character.only = TRUE)}
}
```

When `r NMFSReports::buildTM` run many files are created, but among them is the run.R file. 

```{r, eval=FALSE}
NMFSReports::buildTM()
```

# run.R

```{r, eval=FALSE}
#' ---
#' title: ''
#' author: ''
#' purpose: Run Scripts and R Markdown Files
#' start date: 2021-02-11
#' date modified: YYYY-MM
#' Notes:  
#' ---

######START#######

# Always start with a clean state by removing everything in your environment!
rm(list=ls())
# renv::init()

######***KNOWNS#########
report_title <- ''
report_authors <- ''
report_office_location <- "" 
# For example: 
# "National Oceanic and Atmospheric Administration 
# 1315 East-West Highway [bldg./room]
# Silver Spring, MD 20910"
report_office <- "" # 
report_num <- "###"
report_NOAA_leaders <- "U.S. Department of Commerce
Wynn Coggins, Acting Secretary  

National Oceanic and Atmospheric Administration
Benjamin Friedman, Acting NOAA Administrator
 
National Marine Fisheries Service
Paul Doremus, Acting Assistant Administrator for Fisheries"

#######***WHAT KIND OF OUTPUT#######
#Is this for InDesign? 
designflowin <- FALSE

#######SOURCE SUPPORT SCRIPTS#############

source(here('code', '0_directories.R' ))

source(here('code', '0_functions.R' ))

source(here('code', '0_dataDL.R' ))

source(here('code', '0_data.R' ))



######MAKE REPORT########
cnt.chapt<-"000" # Keep everything in a proper order
plot.list<-c() # This will help us by saving R-ready plots so we can easily go back and edit them if necessary. 
cnt.figures<-0 # This will autoname your figures with consecutive numbers (e.g., Figure 1.)
cnt.tables<-0 # This will autoname your tables with consecutive numbers (e.g., Table 1.)
cnt.equ<-0

#######RUN EACH SECTION#############

# ######***EXAMPLE############
# cnt.chapt<-auto_counter(cnt.chapt) # The order of the chapter in the report
# cnt.chapt.content<-"001" # The order of the content in the report (e.g., figures, images, tables)
# filename0<-paste0(cnt.chapt, "_Example_") #Seperated because we'll need it inside the RMarkdown
# rmarkdown::render(paste0(dir.scripts, "/00_example.Rmd"),
#                   output_dir = dir.chapters,
#                   output_file = paste0(filename0, cnt.chapt.content, "_Text.docx"))



  ############# 1 - frontmatter ####################
  cnt.chapt<-auto_counter(cnt.chapt)
  cnt.chapt.content<-"001" 
  filename0<-paste0(cnt.chapt, "_frontmatter_") 
  rmarkdown::render(paste0(dir.code, "/1_frontmatter.Rmd"),
                    output_dir = dir.chapters,
                    output_file = paste0(filename0, cnt.chapt.content, "_Text.docx"))
                    
  
  
  ############# 2 - abstract ####################
  cnt.chapt<-auto_counter(cnt.chapt)
  cnt.chapt.content<-"001" 
  filename0<-paste0(cnt.chapt, "_abstract_") 
  rmarkdown::render(paste0(dir.code, "/2_abstract.Rmd"),
                    output_dir = dir.chapters,
                    output_file = paste0(filename0, cnt.chapt.content, "_Text.docx"))
                    
  
  
  ############# 3 - introduction ####################
  cnt.chapt<-auto_counter(cnt.chapt)
  cnt.chapt.content<-"001" 
  filename0<-paste0(cnt.chapt, "_introduction_") 
  rmarkdown::render(paste0(dir.code, "/3_introduction.Rmd"),
                    output_dir = dir.chapters,
                    output_file = paste0(filename0, cnt.chapt.content, "_Text.docx"))
                    
  
  
  ############# 4 - methods ####################
  cnt.chapt<-auto_counter(cnt.chapt)
  cnt.chapt.content<-"001" 
  filename0<-paste0(cnt.chapt, "_methods_") 
  rmarkdown::render(paste0(dir.code, "/4_methods.Rmd"),
                    output_dir = dir.chapters,
                    output_file = paste0(filename0, cnt.chapt.content, "_Text.docx"))
                    
  
  
  ############# 5 - results ####################
  cnt.chapt<-auto_counter(cnt.chapt)
  cnt.chapt.content<-"001" 
  filename0<-paste0(cnt.chapt, "_results_") 
  rmarkdown::render(paste0(dir.code, "/5_results.Rmd"),
                    output_dir = dir.chapters,
                    output_file = paste0(filename0, cnt.chapt.content, "_Text.docx"))
                    
  
  
  ############# 6 - discussion ####################
  cnt.chapt<-auto_counter(cnt.chapt)
  cnt.chapt.content<-"001" 
  filename0<-paste0(cnt.chapt, "_discussion_") 
  rmarkdown::render(paste0(dir.code, "/6_discussion.Rmd"),
                    output_dir = dir.chapters,
                    output_file = paste0(filename0, cnt.chapt.content, "_Text.docx"))
                    
  
  
  ############# 7 - workscited ####################
  cnt.chapt<-auto_counter(cnt.chapt)
  cnt.chapt.content<-"001" 
  filename0<-paste0(cnt.chapt, "_workscited_") 
  rmarkdown::render(paste0(dir.code, "/7_workscited.Rmd"),
                    output_dir = dir.chapters,
                    output_file = paste0(filename0, cnt.chapt.content, "_Text.docx"))
                    
  
  
  ############# 8 - workscitedR ####################
  cnt.chapt<-auto_counter(cnt.chapt)
  cnt.chapt.content<-"001" 
  filename0<-paste0(cnt.chapt, "_workscitedR_") 
  rmarkdown::render(paste0(dir.code, "/8_workscitedR.Rmd"),
                    output_dir = dir.chapters,
                    output_file = paste0(filename0, cnt.chapt.content, "_Text.docx"))
                    
  
  

save(plot.list, file=paste0(dir.output.todaysrun, "/plots/reportPlots"))

########***MAKE MASTER DOCX################

#USE GUIDENCE FROM THIS LINK
#https://support.microsoft.com/en-us/help/2665750/how-to-merge-multiple-word-documents-into-one


###############***METADATA##################
# So we can 
#    1. Go back and recreate this exactly with the libraries you used to create this script and 
#    2. Cite the apropriate versions of the packages you used in your report
# More info here: https://rstudio.github.io/packrat/walkthrough.html

CreateMetadata(dir.out = paste0(dir.output.todaysrun, "/metadata"), 
               title = paste0(title0, " Metadata ", Sys.Date()))

# setwd(paste0(dir.output.todaysrun))

```

# Things to change

## Metadata

Update the metadata to include your name, purpose, etc. 

# Knowns

Depending on the type of report, there may be things you want to define the report as a whole. If an annual report, a goot known to add there might be something like ` yr <- 2021 `

# Sections

Actually, what is written in this script is pretty customary and really shouldn't need to be changed unless you changed your mind about the organization of the report. Here, go into each of the .Rmd documents to edit them. 