---
title: "Functions and examples to help you write your report"
date: "`r format(Sys.Date(), format='%B %d %Y') `"
output: rmarkdown::html_vignette
csl: "../inst/cite/bulletin-of-marine-science.csl"
bibliography: "../inst/rmd/bib_example.bib"
vignette: >
  %\VignetteIndexEntry{C_functions-to-help-write-report}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  message = FALSE, echo = TRUE, warning = FALSE, 
  comment = FALSE, collapse = TRUE,
  comment = "#>"
)
options(rmarkdown.html_vignette.check_title = FALSE)

```

```{r setup}
library(NMFSReports)
library(here)
library(magrittr)
library(ggplot2)
library(png)
library(cowplot)
```

This file is essentially the example file included in the `buildReport()` function. 

## From run file:
```{r a}
cnt_chapt <- "000" # Keep everything in a proper order
figure_list <- c() # This will help us by saving R-ready plots so we can easily go back and edit them if necessary. 
table_list <- c() # This will help us by saving R-ready tables  so we can easily go back and edit them if necessary. 
cnt_figures <- 0 # This will autoname your figures with consecutive numbers (e.g., Figure 1.)
cnt_tables <- 0 # This will autoname your tables with consecutive numbers (e.g., Table 1.)
cnt_equ <- 0

cnt_chapt_content<-0
filename0<-"example"
indesign_flowin<-FALSE
```

# Example of how to use this R Markdown document

```{r ChunkName_NameMeAnythingAsLongAsItIsUnique}
# Chunks are were we can write code for something later in the code. 

# example data
dat <- data.frame(x = rnorm(n = 100), 
                y = rnorm(n = 100), 
                col = rep_len(x = c("a", "b"), length.out = 5))

Footnotes.list<-list("ExOfStandardFt" = "Wow, this project is so cool!")

types_of_vessels <- c("NOAA Vessel", "F/V Fishing Boat", "R/V University Vessel", "Private Charter")
```

Here is the report content:

## Systematic writing of content

My example dataset has `r xunits(nrow(dat))` rows in it and `r xunits(ncol(dat))` columns in it.`r paste0("^[", Footnotes.list$ExOfStandardFt,"]") ` 

This sentence exemplifies how to systematically calculate a percent change: `r pchange(start = nrow(dat), end = ncol(dat))`^[Here's another, free-written footnote!]. 

Here are several types of vessels: `r NMFSReports::text_list(types_of_vessels)`. 

## Equations

Here is some equations you'll need to have in this report: 

```{r Eq1}
cnt_equ<-auto_counter(cnt_equ)
```

Eq. `r cnt_equ`: Newton's Universal Law of Gravitation

$$F = G \frac{m_1 m_2}{d^2}$$

```{r Eq2}
cnt_equ<-auto_counter(cnt_equ)
```

Eq. `r cnt_equ`

$$c^2 = b^2 + a^2$$

## Citations

There are a lot of ways to cite within your report, so here is an example of two: [@RN686] and @RN621. Checkout https://github.com/cboettig/knitcitations for more info!

Note that references will appear at the bottom of this document (and any document that you put references in) but when you combine this document with all of the other documents that you create, it will shift to the bottom of the report.

## Example Figure (Plot)

First, create your plot: 

```{r G1a, include = FALSE, comment = FALSE, message = FALSE}
# Edit This:
header <- "Here is a figure!"
footnote<-c("A footnote for this figure!", "A second footnote for this figure!")
nickname <- "example_plot"
  
# Select data and make plot
plot0 <- dat %>%
  ggplot(aes(x = x, y = y, colour = as.factor(col))) + # create plot
  geom_point() 
```

Then, save your plot to the figures folder and create a list object with all of the information you want to store about this plot. 

```{r G1b}
# Don't Edit This:
cnt_chapt_content<-NMFSReports::auto_counter(cnt_chapt_content)
cnt_figures<-cnt_figures + 1

# Systematically save your plot with this simple function
figure_list<-save_figures(figure = plot0, 
                      figure_list = figure_list, 
                      header = header,
                      footnote = footnote,
                      filename0 = filename0, 
                      cnt_chapt_content = cnt_chapt_content, 
                      cnt = cnt_figures, 
                      nickname = nickname,
                      # path = dir_out_figures, 
                      width = 6, # you can change this if you need to...
                      height = 6) # you can change this if you need to...

```

This next chuck will decide if the plot should be printed to the report or not. For InDesign purposes, you would likely not want it to be printed to the word document (hense `indesign_flowin %in% FALSE`). 

```{r G1c, fig.cap=ifelse(indesign_flowin %in% TRUE, "", figure_list[[length(figure_list)]]$caption)}
# Print or Don't Print Plot in Text
# You don't want to print this in the document if this text will be flowed into InDesign. 
# However, sometimes its nice to see everything all together, so this variable is 
# something you might like to toggle on and off. 
# Hense, FALSE = print here, TRUE = don't print here, just make the .pdf (coded above)
if (indesign_flowin %in% FALSE) { 
  plot0 # print plot in text
} else if (indesign_flowin %in% TRUE){ # for reports that need to be flowed into InDesign 
  rmarkdown::render(TableFigureHeader, 
                    quiet = TRUE,
                  output_dir = dir_chapters, 
                  output_file = paste0(filename00,cnt_chapt_content,"_Title.docx"))
}
```

Here in plot `r ref_figtab(list_obj = figure_list, nickname = "example_plot", sublist = "number")`, we see that...


## Example Figure (Reference Image)

```{r G2a, include = FALSE, comment = FALSE, message = FALSE}
# Edit This:
header <- "Here is a figure!"
footnote<-c("A footnote for this figure!")
nickname <- "noaalogo"

# Select data and make plot
plot0 <- 
  cowplot::ggdraw() +
  cowplot::draw_image(readPNG(here::here("inst", "img", "noaa-gray.png"))) 
```


```{r G2b}
# Don't Edit This:
cnt_chapt_content<-auto_counter(cnt_chapt_content)
cnt_figures<-cnt_figures+1

# Systematically save your plot with this simple function
figure_list<-save_figures(figure = plot0, 
                      figure_list = figure_list, 
                      header = header,
                      footnote = footnote,
                      filename0 = filename0, 
                      cnt_chapt_content = cnt_chapt_content, 
                      cnt = cnt_figures, 
                      nickname = nickname,
                      # path = dir_out_figures, 
                      width = 1, # you can change this if you need to...
                      height = 1,  # you can change this if you need to...
                      filename_desc = "noaalogo")

```


```{r G2c, fig.cap=ifelse(indesign_flowin %in% TRUE, "", figure_list[[length(figure_list)]]$caption)}
# Print or Don't Print Plot in Text
# You don't want to print this in the document if this text will be flowed into InDesign. 
# However, sometimes its nice to see everything all together, so this variable is 
# something you might like to toggle on and off. 
# Hense, FALSE = print here, TRUE = don't print here, just make the .pdf (coded above)
if (indesign_flowin %in% FALSE) { 
  plot0 # print plot in text
} else if (indesign_flowin %in% TRUE){ # for reports that need to be flowed into InDesign 
  rmarkdown::render(TableFigureHeader, 
                    quiet = TRUE,
                  output_dir = dir_chapters, 
                  output_file = paste0(filename00,cnt_chapt_content,"_Title.docx"))
}
```

Here in figure `r ref_figtab(list_obj = figure_list, nickname = "noaalogo", sublist = "number")`, we see the NOAA logo. 


## Example Table (Basic)

```{r T1a}
# Edit This:
header <- "Here is a table!"
footnote<-"A footnote for this table!"
nickname <- "example1" # this is so you can refer to it later systematically

# Select data and make plot
table_raw<-data.frame(col = LETTERS[1:10], 
                      x = rnorm(n = 10), 
                y = rnorm(n = 10)) 
table_print <- table_raw
table_print[,c("x", "y")] <- NMFSReports::mod_number(table_print[,c("x", "y")], 
                                                     divideby = 1, 
                                                     comma_seperator = TRUE, 
                                                     digits = 2)

```


```{r T1b}
# Don't Edit This:
cnt_chapt_content<-auto_counter(cnt_chapt_content)
cnt_tables<-cnt_tables+1

# Systematically save your plot with this simple function
table_list<-save_tables(table_raw = table_raw, 
                        table_print = table_print, 
                        table_list = table_list, 
                        header = header,
                        footnote = footnote,
                        filename0 = filename0,
                        nickname = nickname,
                        cnt_chapt_content = cnt_chapt_content, 
                        cnt = cnt_tables#, 
                        # path = dir_out_tables
                        )
```


```{r T1c, fig.cap=ifelse(indesign_flowin %in% TRUE, "", table_list[[length(table_list)]]$caption)}

# Print or Don't Print Table in Text
# You don't want to print this in the document if this text will be flowed into InDesign. 
# However, sometimes its nice to see everything all together, so this variable is something you might like to toggle on and off. Hense, FALSE = print here, TRUE = don't print here, just make the .pdf (coded above)
if (indesign_flowin %in% FALSE) {
  table_print %>%
          format_cells(rows = 0, # make column names
                       cols = 1:ncol(table_print), # for all columns
                       fonttype = "bold") %>% # bold
          knitr::kable(row.names = FALSE, booktabs = TRUE) #print table in text
}
```

Here in table `r ref_figtab(list_obj = table_list, nickname = "example1", sublist = "number")`, we see that...

## Example Table (With Footnotes)

```{r T2a}
# Edit This:
header <- "Here is a table!"
footnote<-"A footnote for this table!"
nickname <- "example_foot"

# Select data
table_raw<-data.frame(col = LETTERS[1:10], 
                      x = rnorm(n = 10), 
                y = rnorm(n = 10), 
                footnotes = NA) 

table_raw$footnotes[3]<-"Example footnote in a table 1."
table_raw$footnotes[4]<-"Example footnote in a table 2.&&&Example footnote in a table 3."
table_print <- table_raw
table_print[,c("x", "y")] <- NMFSReports::mod_number(table_print[,c("x", "y")], 
                                                     divideby = 1, 
                                                     comma_seperator = TRUE, 
                                                     digits = 2)

# example of how to add footnotes from a column of footnotes
# here, we'll add footnotes from the "footnotes" column to the content in the first column, where necessary
table_print <- add_table_footnotes(tab = table_print, 
                             from_col = "footnotes", # either use the name of the column
                             to_col = 1) # or the number of that column in that table

# here, I'll add a specific footnote to a specific place in the table
table_print <- add_table_footnotes(tab = table_print, 
                                   footnote = "Example footnote in a table 4.", 
                             to_row = 2, 
                             to_col = 2)

table_print <- add_table_footnotes(tab = table_print, 
                                   footnote = c("Example footnote in a table 5.", 
                                                "Example footnote in a table 6."), 
                             to_row = 4, 
                             to_col = 2)

table_print$footnotes<-NULL # remove column from final table

```


```{r T2b}
# Don't Edit This:
cnt_chapt_content<-auto_counter(cnt_chapt_content)
cnt_tables<-cnt_tables+1
nickname <- "example_foot" # this is so you can refer to it later systematically

# Systematically save your plot with this simple function
table_list<-save_tables(table_raw = table_raw, 
                        table_print = table_print, 
                        table_list = table_list, 
                        header = header,
                        footnote = footnote,
                        filename0 = filename0, 
                        nickname = nickname,
                        cnt_chapt_content = cnt_chapt_content, 
                        cnt = cnt_tables#, 
                        # path = dir_out_tables
                        )
```


```{r T2c, fig.cap=ifelse(indesign_flowin %in% TRUE, "", table_list[[length(table_list)]]$caption)}

# Print or Don't Print Table in Text
# You don't want to print this in the document if this text will be flowed into InDesign. 
# However, sometimes its nice to see everything all together, so this variable is something you might like to toggle on and off. Hense, FALSE = print here, TRUE = don't print here, just make the .pdf (coded above)
if (indesign_flowin %in% FALSE) {
  table_print %>%
          format_cells(rows = 0, # make column names
                       cols = 1:ncol(table_print), # for all columns
                       fonttype = "bold") %>% # bold
          knitr::kable(row.names = FALSE, booktabs = TRUE) #print table in text
}
```


Here in table `r ref_figtab(list_obj = table_list, nickname = "example_foot", sublist = "number")`, we see that...

## References

