---
title: "Functions in Action to Help You Write Your Report"
author: Emily Markowitz (Emily.Markowitz AT NOAA.gov / EmilyMarkowitz-NOAA)
date: "`r format(Sys.Date(), format='%B %d %Y') `"
output: 
  html_document:
    standalone: true
    smart: true
    normalize: true
    toc: true
    highlight: tango
    self-contained: true
    theme: cerulean
  pdf_document:
    toc: true
    highlight: tango
vignette: >
  %\VignetteIndexEntry{C_functions-to-help-write-report}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(message = FALSE, echo = TRUE, warning = FALSE, 
  collapse = TRUE,
  comment = "#>"
)

TF<-FALSE
```

```{r setup}
PKG <- c(# devtools::install_github("emilymarkowitz-NOAA/NMFSReports", force = TRUE)
         "NMFSReports",
         
         # Data Managment
         "filesstrings", 
         "data.table", 
         "plyr",  
         "tidyverse",

         # #RMarkdown
         "rmarkdown",
         "kableExtra"
)

for (p in PKG) {
  if(!require(p,character.only = TRUE)) {  
    install.packages(p, repos = "http://cran.us.r-project.org")
    require(p,character.only = TRUE)}
}
```


## From run file: 
```{r a}
cnt.chapt<-"000" # Keep everything in a proper order
plot_list<-c() # This will help us by saving R-ready plots so we can easily go back and edit them if necessary. 
cnt_figures<-0 # This will autoname your figures with consecutive numbers (e.g., Figure 1.)
cnt.tables<-0 # This will autoname your tables with consecutive numbers (e.g., Table 1.)
cnt.equ<-0
counter.inside<-0
cnt_chapt_content<-0
filename0<-"example"
designflowin<-FALSE
```

Here is the report content!

## Example Text 

```{r b}
# Don't forget to load your example data!
dat <- datasets::beaver1
head(dat)

# And some footnotes you might reuse throughout your report
Footnotes.list<-list(ExOfStandardFt = "A footnote!")
```

My example dataset has `r xunits(nrow(dat))` rows in it and `r xunits(ncol(dat))` columns in it.`r paste0("^[", Footnotes.list$ExOfStandardFt,"]") ` That is `r pchange(start = nrow(dat), end = ncol(dat))`^[Here's another, free-written footnote!]. 

## Equations

Here is some equation you'll need to have in this report, of which produces the variable $X$. 

```{r Eq1}
cnt.equ<-auto_counter(cnt.equ)
```

Eq. `r cnt.equ`

$$X = Y + Z$$

## Example Figure

```{r G1a}
# Don't Edit This:
cnt_chapt_content<-auto_counter(cnt_chapt_content)
cnt_figures<-cnt_figures+1
```


```{r G1b}
# Edit This:
Header<-paste0("Figure ",cnt_figures,". Here's a plot")
Footnotes<-"A footnote for this figure!"

# Select data and make plot
dat1<-dat[dat$day %in% 346,]
plt<-qplot(x = dat1$time, y = dat1$temp, col = as.factor(dat1$activ)) #+ # create plot
   # nmfspalette::scale_color_nmfs() # Use NMFS Color Pallet

```


```{r G1c}
# Don't Edit This:
Header<-str_to_sentence(Header)
Title0<-paste0(Header, "^[", Footnotes, "]")
filename00<-paste0(filename0, cnt_chapt_content, "_Fig_",cnt_figures)

if (designflowin %in% T){
  cnt_chapt_content<-funct_counter(cnt_chapt_content)
  rmarkdown::render(TableFigureHeader, 
                    quiet = T,
                  output_dir = dir.chapters, 
                  output_file = paste0(filename00,cnt_chapt_content,"_Title.docx"))
}
```


```{r G1d, fig.cap=ifelse(designflowin %in% T, "", Title0)}
# Don't Edit This:

# Systematically save your plot with this simple function
plot_list<-SaveGraphs(plot0 = plt, plot_list = plot_list, 
           filename0 = filename0, 
           Header = Title0,
           cnt_chapt_content = cnt_chapt_content, 
           cnt_figures = cnt_figures, 
           path = NULL, #dir.chapters, 
           width = 6, 
           height = 6) # but you can change this if you need...

# Print or Don't Print Plot in Text
# You don't want to print this in the document if this text will be flowed into InDesign. 
# However, sometimes its nice to see everything all together, so this variable is something you might like to toggle on and off. Hense, FALSE = print here, TRUE = don't print here, just make the .pdf (coded above)
if (designflowin %in% FALSE) { 
  plt #print plot in text
}
```






