---
title: "Use {googledrive} to access documents from Google Drive made collaboratively with coworkers"
date: "`r format(Sys.Date(), format='%B %d %Y') `"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{D_googledrive}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
  
```{r, include = FALSE}
knitr::opts_chunk$set(
  message = FALSE, echo = TRUE, warning = FALSE, 
  comment = FALSE, collapse = TRUE,
  comment = "#>"
)
options(rmarkdown.html_vignette.check_title = FALSE)
```

```{r setup}
library(NMFSReports)
library(here)
library(ggplot2)
# library(googledrive)
# library(XML)
```


A great resource for this is from [https://googledrive.tidyverse.org/](tidyverse). As long as you have access to a given spreadsheet or google doc file, you can easily and quickly download it using the the code below. You'll need to set up an API token, but it is just a few steps. 

Once accessed, the file will be saved to your directory and can be accessed for future use. 

# Google Spreadsheets

[https://docs.google.com/spreadsheets/d/1U3LvtKOwSlZ_-6KFJDYLWUPGkASWxovETk7lihxHnUA/edit?usp=sharing](Here is a test document to play with.) 

```{r, eval = FALSE}
library("googledrive")

drive_deauth()
drive_auth()
1 # Using the first token you have.

googledrive::drive_download("test123123_spreadsheet", # Must be a unique name
               type = "csv", 
               overwrite = TRUE, 
               path = "./test123123_spreadsheet")

a<-readr::read_csv("test123123_spreadsheet.csv")
kable(a)
```

# Google Docs

[https://docs.google.com/document/d/1ebCqXHqPHYXfRN87qs8pTULA8_4W25yh4gTMSo5WB4E/edit?usp=sharing](Here is a test document to play with.) 

```{r, eval = FALSE}

filename00 <- "test123123_doc"

out_new<-paste0(dir_out_rawdata, filename00, ".zip")

# Make a temporary file to content save to
temp <- tempfile(fileext = ".zip")

dl <- googledrive::drive_download(file = filename00,
  path = temp, overwrite = TRUE)
1

out <- unzip(temp, exdir = tempdir())

file.rename(from = out,
            to = out_new)

spp_content<-XML::htmlTreeParse(out_new, useInternal = TRUE)

spp_content <- xpathApply(spp_content, "//body//text()[not(ancestor::script)][not(ancestor::style)][not(ancestor::noscript)]", xmlValue)

x <- paste(cat(unlist(spp_content)))

write.table(x = x, 
            file = paste0("./", filename00, ".txt"))
```


` cat(unlist(spp_content)) `

