---
output:
  word_document:
    pandoc_args: ["--metadata-file=header.yaml"]
    reference_docx: styles_reference.docx
    df_print: kable
csl: "../cite/citestyle.csl"
bibliography: "../cite/bibliography.bib"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, 
  include = TRUE,
  warning = FALSE, 
  error = FALSE, 
  message = FALSE)

# # In case you want to run this outside of the run.R structure
# library(NMFSReports)
# library(magrittr)
# library(ggplot2)
# library(nmfspalette)
# library(magick)
# library(PNG)
# cnt_equ <- 0
# cnt_fig <- 0
# cnt_chapt_content <- 0
# cnt_figures <- 0
# dir_code <- "C:/Users/Emii/Documents/Homework/2Utilities/NMFSReports/inst/rmd/"
# dir_out_figures <- "./"
# figure_list <- list()
# indesign_flowin<-FALSE
```

# Example of how to use this R Markdown document

```{r ChunkName_NameMeAnythingAsLongAsItIsUnique}
# Chunks are were we can write code for something later in the code. 

# example data
dat <- data.frame(x = rnorm(n = 100), 
                y = rnorm(n = 100), 
                col = rep_len(x = c("a", "b"), length.out = 5))

Footnotes.list<-list("ExOfStandardFt" = "Wow, this project is so cool!")

types_of_vessels <- c("NOAAS Vessel", "F/V Fishing Boat", "R/V University Vessel", "Private Charter")
```

Here is the report content:

## Systematic writing of content

My example dataset has `r xunits(nrow(dat))` rows in it and `r xunits(ncol(dat))` columns in it.`r paste0("^[", Footnotes.list$ExOfStandardFt,"]") ` 

This sentance examplifies how to systematically calculate a percent change: `r pchange(start = nrow(dat), end = ncol(dat))`^[Here's another, free-written footnote!]. 

Here are several types of vessels: `r NMFSReports::text_list(types_of_vessels)`. 

## Equations

Here is some equation you'll need to have in this report, of which produces the variable $X$. 

```{r Eq1}
cnt_equ<-auto_counter(cnt_equ)
```

Eq. `r cnt_equ`

$$X = Y + Z$$


## Citations

There are a lot of ways to cite within your report, so here is an example of two: [@RN686] and @RN621. Checkout https://github.com/cboettig/knitcitations for more info!

Note that references will appear at the bottom of this document (and any document that you put references in) but when you combine this document with all of the other documents that you create, it will shift to the bottom of the report.

## Example Figure (Plot)

```{r G1a}
header <- "Here is a figure!"
footnote <- c("A footnote for this figure!", "A second footnote for this figure!")
nickname <- "example_plot"
  
# Select data and make plot
figure <- dat %>%
  ggplot(aes(x = x, y = y, colour = as.factor(col))) + # create plot
  geom_point() +
  theme_classic() +
  # theme(text=element_text(family="Times New Roman")) + 
  nmfspalette::scale_color_nmfs(palette = "coral") # Use NMFS Color Pallet

```

```{r G1b, child = system.file("rmd/_child_save_fig.Rmd", package = "NMFSReports")}
# save yo' stuff and do a lot of behind the scenes work
# alt: check out the "child = " in this chunk header (which must stay empty)
```

Here in plot `r ref_figtab(list_obj = figure_list, nickname = "example_plot", sublist = "number")`, we see that...

## Example Figure (Refernce Image)

```{r G2a, include = FALSE, comment = FALSE, message = FALSE}
header <- "Here is a figure!"
footnote<-c("A footnote for this figure!")
filename_desc <- "noaalogo"
nickname <- "example_logo"

# Select data and make plot
figure <- 
  cowplot::ggdraw() +
  cowplot::draw_image(readPNG(here::here("img", "noaa-gray.png"))) 

# save yo' stuff and do a lot of behind the scenes work
# alt: this does the same thing as calling "child = " in the chunk header
res <- knitr::knit_child(
  text = knitr::knit_expand(
    file = system.file("rmd/_child_save_fig.Rmd", package = "NMFSReports")
  ),
  quiet = TRUE
)
```

`r res `

## Example Table (Basic)

```{r T1a, include = FALSE, comment = FALSE, message = FALSE}
header <- "Here is a table!"
footnote<-"A footnote for this table!"
nickname <- "example1" # this is so you can refer to it later systematically

# Select data and make plot

# Create data-saver version of table that will be used to reference things later saved as backup
table_raw<-data.frame(col = LETTERS[1:10], 
                      x = rnorm(n = 10), 
                      y = rnorm(n = 10)) 

# Create pretty version of table that will go into report
table_print <- table_raw
table_print[,c("x", "y")] <- 
  NMFSReports::mod_number(table_print[,c("x", "y")], 
                          divideby = 1, 
                          comma_seperator = TRUE, 
                          digits = 2)

# Format table 
table_print <- table_print %>%
          format_cells(rows = 0, # make column names
                       cols = 1:ncol(table_print), # for all columns
                       fonttype = "bold") %>% # bold
          knitr::kable(row.names = FALSE, booktabs = TRUE) #print table in text

```

```{r T1b, child = system.file("rmd/_child_save_tab.Rmd", package = "NMFSReports")}
# save yo' stuff and do a lot of behind the scenes work
# alt: check out the "child = " in this chunk header (which must stay empty)
```

Here in plot `r ref_figtab(list_obj = table_list, nickname = "example1", sublist = "number")`, we see that...

## Example Table (With Footnotes)

```{r T2a}
header <- "Here is a table!"
footnote<-"A footnote for this table!"
nickname <- "example_foot" # this is so you can refer to it later systematically

# Select data and make plot

# Create data-saver version of table that will be used to reference things later saved as backup
table_raw<-data.frame(col = LETTERS[1:10], 
                      x = rnorm(n = 10), 
                y = rnorm(n = 10), 
                footnotes = NA) 

table_raw$footnotes[3]<-"Example footnote in a table 1."
table_raw$footnotes[4]<-"Example footnote in a table 2.&&&Example footnote in a table 3."

# Create pretty version of table that will go into report
table_print <- table_raw
table_print[,c("x", "y")] <- NMFSReports::mod_number(table_print[,c("x", "y")], 
                                                     divideby = 1, 
                                                     comma_seperator = TRUE, 
                                                     digits = 2)

# example of how to add footnotes from a column of footnotes
# here, we'll add footnotes from the "footnotes" column to the content in the first column, where necessary
table_print <- add_table_footnotes(tab = table_print, 
                             from_col = "footnotes", # either use the name of the column
                             to_col = 1) # or the number of that column in that table

# here, I'll add a specific footnote to a specific place in the table
table_print <- add_table_footnotes(tab = table_print, 
                                   footnote = "Example footnote in a table 4.", 
                             to_row = 2, 
                             to_col = 2)

table_print <- add_table_footnotes(tab = table_print, 
                                   footnote = c("Example footnote in a table 5.", 
                                                "Example footnote in a table 6."), 
                             to_row = 4, 
                             to_col = 2)

table_print$footnotes<-NULL # remove column from final table

# Format table
table_print <- table_print %>%
          format_cells(rows = 0, # make column names
                       cols = 1:ncol(table_print), # for all columns
                       fonttype = "bold") # bold

# save yo' stuff and do a lot of behind the scenes work
# alt: this does the same thing as calling "child = " in the chunk header
res <- knitr::knit_child(
  text = knitr::knit_expand(
    file = system.file("rmd/_child_save_tab.Rmd", package = "NMFSReports")
  ),
  quiet = TRUE
)
```

`r res `

Here in table `r ref_figtab(list_obj = table_list, nickname = "example_foot", sublist = "number")`, we see that...
